### 2016-01-30 paper/main.tex
Fix minor typos in paper/main.tex

For the likelihood $p(\bhat | \beta, \shat)$ we assume  
\begin{equation} \label{eqn:normlik}
p(\bhat | \beta, \shat) = \prod_j N(\bhat_j; \beta_j, \shat_j^2).
\end{equation}
Here, in additional to some conditional independence assumptions, we are 
effectively  assuming that the number of observations used to compute $\bhat_j,\shat_j$ are sufficiently large to justify a normal approximation.

@@

There are two key differences between our approach and all of these three existing methods. First, 
whereas these existing methods summarize the information on $\beta_j$ by a single number -- either a $z$ score (\locfdr and \mixfdr), or a $p$ value (\qvalue) -- 
we instead work with two numbers ($\bhat_j,\shat_j$). Here we are building on \cite{wakefield:2009}, who develops Bayesian tests 
for individual null hypotheses using these two numbers, using the normal approximation \ref{eqn:normlik}; see also \cite{efron1993bayes}.
Using two numbers instead of one clearly has the potential to be more informative, and indeed, results later (Figure \ref{fig:goodpoor}) illustrate 
how it can improve performance by taking better account of variation in measurement precision among observations.
%(And in the special case where $\shat_j$ are equal for all $j$, our approach essentially comes down to the same thing as these existing methods.)
% Or more generally Section xx illustrates the potential practical effects

@@

The model \ref{eqn:beta-alpha} for general $\alpha$ can be fitted using the algorithm for $\alpha=0$. 
To see this, define $b_j:= \beta_j/ \shat_j^\alpha$, and $\hat{b} := \bhat_j/\shat_j^\alpha$. Then $\hat{b}_j$ is an estimate of $b_j$ with
 standard error $\shat'_j:=\shat_j^{1-\alpha}$. 
 Applying the algorithm for $\alpha=0$ to effect estimates $\hat{b}_1,\dots,\hat{b}_J$ with standard errors $\shat'_1,\dots,\shat'_J$
yields a posterior distribution $p(b_j | \shat_j, \hat{b}_j, \hat{\pi}, \alpha)$, which induces a posterior distribution on $\beta_j = b_j \shat_j^\alpha$.
%In the special case $\alpha=1$, $\hat{b}_j$ is the $t$ score $t_j$ and $\shat'{b}=1$, so this involves applying our algorithm to the $t$ scores
%treating them all as having the same standard error. In this case the local fdr from our method becomes monotonic in each direction as
%the $t$ score increases away from zero, just as with \qvalue, and (usually) \mixfdr and \locfdr.

>>>>

For the likelihood $p(\bhat | \beta, \shat)$ we assume  
\begin{equation} \label{eqn:normlik}
p(\bhat | \beta, \shat) = \prod_j N(\bhat_j; \beta_j, \shat_j^2).
\end{equation}
Here, in addition to some conditional independence assumptions, we are 
effectively  assuming that the number of observations used to compute $\bhat_j,\shat_j$ are sufficiently large to justify a normal approximation.

@@

There are two key differences between our approach and all of these three existing methods. First, 
whereas these existing methods summarize the information on $\beta_j$ by a single number -- either a $z$ score (\locfdr and \mixfdr), or a $p$ value (\qvalue) -- 
we instead work with two numbers ($\bhat_j,\shat_j$). Here we are building on \cite{wakefield:2009}, who develops Bayesian tests 
for individual null hypotheses using these two numbers, using the normal approximation (\ref{eqn:normlik}); see also \cite{efron1993bayes}.
Using two numbers instead of one clearly has the potential to be more informative, and indeed, results later (Figure \ref{fig:goodpoor}) illustrate 
how it can improve performance by taking better account of variation in measurement precision among observations.
%(And in the special case where $\shat_j$ are equal for all $j$, our approach essentially comes down to the same thing as these existing methods.)
% Or more generally Section xx illustrates the potential practical effects

@@

The model (\ref{eqn:beta-alpha}) for general $\alpha$ can be fitted using the algorithm for $\alpha=0$. 
To see this, define $b_j:= \beta_j/ \shat_j^\alpha$, and $\hat{b} := \bhat_j/\shat_j^\alpha$. Then $\hat{b}_j$ is an estimate of $b_j$ with
 standard error $\shat'_j:=\shat_j^{1-\alpha}$. 
 Applying the algorithm for $\alpha=0$ to effect estimates $\hat{b}_1,\dots,\hat{b}_J$ with standard errors $\shat'_1,\dots,\shat'_J$
yields a posterior distribution $p(b_j | \shat_j, \hat{b}_j, \hat{\pi}, \alpha)$, which induces a posterior distribution on $\beta_j = b_j \shat_j^\alpha$.
%In the special case $\alpha=1$, $\hat{b}_j$ is the $t$ score $t_j$ and $\shat'{b}=1$, so this involves applying our algorithm to the $t$ scores
%treating them all as having the same standard error. In this case the local fdr from our method becomes monotonic in each direction as
%the $t$ score increases away from zero, just as with \qvalue, and (usually) \mixfdr and \locfdr.
